SMT-Boosted Security Types for Low-Level MPC

### 2025-11-11 toplas26/metaty.tex
checkpoint

In the rules for share type annotations of the form $\notg{\stt} :
\sty$,

>>>>

Programmers can also specify bindings for local computations, for
example if $\mx{x}{1},\mx{x}{2}$ are shares obtained by, e.g., local
homomorphic addition, the programmer can specify
$[\mx{x}{1},\mx{x}{2}] : \sharety$. This supports compositionality of
type checking. Thus, in the rules for share type annotations of the
form $\notg{\stt} : \sty$, we have different rules for checking local and interactive
$\sharety$ type ascriptions (\TirName{LocalShares} and \TirName{GenShares},
respectively), and for checking local and interactive
$\pubty$ type ascriptions (\TirName{LocalPublic} and \TirName{MaskedPublic},
respectively). Observe the use of definitions $\xdefs$ to refer to
SMT equivalences, and the use of $\Vdash$ to verify share typing.
